SunPy - Python for Solar Physics

### 2014-01-28 1-Introduction.tex
edited first paragraph in intro

\section{Introduction}
Science, including solar physics and astrophysics, is driven by the analysis 
and summarizing of data. Modern advances in sensor technology combined with 
the availability of cheap storage and large bandwidth communications has led to 
a rapid and overwhelming increase in amount of data for scientists to analyse.
For example, NASA's Solar 
Dynamics Observatory (SDO) satellite records over 1 TB of data per day. Analysing this 
mountain of data to enable scientific discovery requires increasingly complex software 
tools. Standardised, easy-to-use,
and transparent software tools are a key enabling technology
so that the scientific community can build upon a common foundation.
%schriste - the opening paragraph still needs work

>>>>

\section{Introduction}

Science is driven by the analysis of data. Modern advances in sensor
technology combined with the availability of cheap storage has led to
rapid increases in amount of data available to scientists in almost
every discipline.  Solar physics is no exception to this trend. NASA's
Solar Dynamics Observatory (SDO) satellite, launched in February 2010,
produces over 1 TB of catalogued and stored data per day. Managing and
analysing this mountain of data to enable scientific discovery
requires increasingly sophisticated software tools.  Key qualities
that these tools should have include robustness, ease of use, a
transparent development history, ease of modification, and conformance
to standards.  Software with these qualities provides a strong
foundation which is responsive to the needs of the community as data
volumes grow and science questions evolve.
%schriste - the opening paragraph still needs work
%ji - I had a go.
